Concurrent Programming with CXL

### 2020-05-17 book/paper.tex
Refining the progress property

Mutual exclusion is an example of a \emph{safety property}, a
property that ensures that \emph{nothing bad will happen}, in this case
two processes being in the critical section.
What we need now a \emph{liveness property}: we want to ensure that
\emph{eventually something good will happen}.
There are various possible liveness properties we could use,
but here we will propose the following informally: when no process is in the
critical section, then any process that tries should be able to
enter the critical section.  We call this \emph{progress}.

>>>>

Mutual exclusion is an example of a \emph{safety property}, a
property that ensures that \emph{nothing bad will happen}, in this case
two processes being in the critical section.
What we need now a \emph{liveness property}: we want to ensure that
\emph{eventually something good will happen}.
There are various possible liveness properties we could use,
but here we will propose the following informally: when every process
that is in the critical section eventually leaves it, then any process
that tries to enter the critical section should eventually be able to do so.
We call this \emph{progress}.
